Automated Topic Naming

### 2011-09-06 ese/ese.tex
some editting

In PostgreSQL, by comparison, the frequencies seem to by cyclic, since we are not studying a maintenance-phase for the product, but rather ongoing
feature addition and usability improvements.

\subsection{Do Projects Differ in their Relative  Topic Interest?}
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and	
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
PostgreSQL had more NFR topics in general, but \emph{portability},
\emph{functionality} and \emph{usability} were more prevalent in
PostgreSQL. One notable difference between PostgreSQL and the other
two projects is that many of the commits for PostgreSQL were UI
changes and documentation changes. PostgreSQL also seemed to focus
more on reliability later in the case than earlier like MySQL.
In all cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers
how often portability arises as a concern.

@@

We wanted to see how similar developers were to each other in terms of
the NFRs that worked on. First we did pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair and we
found that $3/10$ of these tests the developers were significantly
different, that is their distributions were not similar. This implies
that there are authors who focus on different NFRs or different
proportion of NFRs.

In Figure \ref{fig:authorcluster} we clustered developers using the
Ward method of Hierarchical clustering.  This diagram shows that
\texttt{petere}, \texttt{tgl} and \texttt{momjian} form their own
cluster (they are also the most frequent committers). This is
interesting because it means that the important developers are not
committing code that fits the same NFR profile. In terms of the larger
cluster we can see that \texttt{momjian} and \texttt{tgl} are in the
same cluster, but \texttt{petere} is not. The most frequent
committers do not share the same clusters. This implies that
developers do work on different sets of NFRs and have different
software quality focus.

Figure \ref{fig:authorcluster} clustered the authors into $2$ clusters
and $6$ clusters. We chose $6$ because the difference in width between
entities and centroids was minimal at $6$ and the derivative of was
the highest in that region as well.

It should be noted that much of PostgreSQL development originates from
the mailinglist and the developers are often pushing integrations. If
we compare the total to each author we find that 1 quarter of the
authors have a similarity of $0.47$ or less. This is depicted in
Figure \ref{fig:authorsim} where we can see that not all authors are
as similar to the global trend as others. Of
course, we found that number of commits had a strong correlation
($0.59$ Pearson) between the similarity to the aggregate and the
number of topics associated with that author.

@@

Given the top 15 PostgreSQL devs we found that proportionally many
devs had a focus on NFR topics. Authors with top proporitions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that yes indeed there was often a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.

>>>>

In PostgreSQL, by comparison, the frequencies seem to be cyclic, since we are not studying a maintenance-phase for the product, but rather ongoing
feature addition and usability improvements.

\subsection{Do Projects Differ in their Relative  Topic Interest?}
\emph{Yes}. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and	
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
PostgreSQL had more NFR topics in general, but \emph{portability},
\emph{functionality} and \emph{usability} were more prevalent in
PostgreSQL. One notable difference between PostgreSQL and the other
two projects is that many of the commits for PostgreSQL were UI
changes and documentation changes. PostgreSQL also seemed to focus
more on \emph{reliability} later in the case study than earlier like MySQL.
In all cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers
how often \emph{portability} arises as a concern.

@@

We wanted to see how similar developers were to each other in terms of
the NFRs that worked on. 
Within this section we focused on PostgreSQL.
First we did pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair and we
found that $3/10$ of these tests the developers were significantly
different, that is their distributions were not similar. This implies
that there are authors who focus on different NFRs or different
proportion of NFRs.

In Figure \ref{fig:authorcluster} we clustered the top developers from
PostgreSQL using the
Ward method of Hierarchical clustering.  This diagram shows that
\texttt{petere}, \texttt{tgl} and \texttt{momjian} form their own
cluster (they are also the most frequent committers). This is
interesting because it means that the important developers are not
committing code that fits the same NFR profile. In terms of the larger
cluster we can see that \texttt{momjian} and \texttt{tgl} are in the
same cluster, but \texttt{petere} is not. The most frequent
committers do not share the same clusters. This implies that
developers do work on different sets of NFRs and have different
software quality focus.

Figure \ref{fig:authorcluster} clustered the authors into $2$ clusters
and $6$ clusters. We chose $6$ because the difference in distance
between entities and centroids was minimal at $6$ clusters, and the
derivative of distance was the highest in that region as well.

It should be noted that much of PostgreSQL development originates from
the mailinglist and the developers are often pushing integrations. If
we compare the global NFR distribution to each author we find that 1
quarter of the authors have a similarity of $0.47$ or less. This is
depicted in Figure \ref{fig:authorsim} where we can see that not all
authors are as similar to the global trend as others. Of course, we
found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson).

@@

Given the top 15 PostgreSQL developers we found that proportionally many
developers had a focus on NFR topics. Authors with top proporitions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that yes indeed there was often a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.
